% !TEX root = ../thesis.tex
%=========================================================
\chapter{Superconducting Transport}
\label{ch:superconducting-transport}
%=========================================================

    Superconductivity was first observed by Heike Kamerlingh Onnes in 1911, when the electrical resistance of mercury vanished abruptly upon cooling below 4.2\,K. Shortly thereafter, the Meissner--Ochsenfeld effect revealed that superconductors also expel magnetic fields, establishing the two defining macroscopic properties of this quantum state of matter: perfect conductivity and perfect diamagnetism. \cite{onnes_further_1991, meissner_neuer_1933}

    At its core, superconductivity originates from an effective attraction between electrons near the Fermi surface. When an electron moves through the metal, it slightly distorts the ion lattice, creating a transient region of enhanced positive charge. A second electron can be attracted to this distortion, resulting in a very weak but cooperative pairing mechanism mediated by lattice vibrations (phonons). Despite the underlying Coulomb repulsion, this mechanism allows pairs of electrons with opposite momentum and spin to form Cooper-pairs. When many such pairs form simultaneously, they condense into a coherent macroscopic quantum state capable of carrying electrical current without resistance.

    The remainder of this chapter develops a comprehensive theoretical framework for superconducting transport from four complementary viewpoints. These perspectives differ in the degrees of freedom they emphasize quasi-particles, phase dynamics, transparency channels, and environmental fluctuations. Together form a consistent and unified picture of the phenomena observed in experiment.

    The first part introduces the microscopic Bardeen--Cooper--Schrieffer theory. It describes how electrons near the Fermi surface pair in the weak-coupling limit, how this pairing leads to an energy gap and a characteristic quasi-particle density of states, and how these quantities manifest in tunneling spectroscopy and photon-assisted transport.

    The second part presents the macroscopic Ginzburg--Landau description, where the superconducting condensate is represented by a complex order parameter with a well-defined phase. Spatial variations of this phase control the behavior of weak links and give rise to the Josephson effects, Shapiro steps, and the influence of dissipation and capacitance captured by the RCSJ model.

    The third part provides the mesoscopic description, which connects microscopic quasi-particle physics with macroscopic phase coherence. Here, Andreev reflection and multiple Andreev reflections govern charge transport in highly transparent contacts, and the resulting \textit{I--V} characteristics encode the microscopic transmission properties of the junction.

    Finally, the stochastic description accounts for phase fluctuations in dissipative electromagnetic environments through \textit{P(E)}-theory. This framework captures how the impedance of the surrounding circuitry affects phase coherence, energy exchange, and the overall \textit{I--V} characteristics.

    Before turning to the detailed microscopic, macroscopic, mesoscopic, and stochastic descriptions, the following two subsections introduce the global definitions used throughout this chapter: the material platform (aluminum) and the general microwave drive model applied in all driven-transport scenarios.
    
    \subsubsection*{Aluminum as a Model BCS Superconductor}

        Throughout this chapter, aluminum serves as the representative weak-coupling BCS superconductor. It possesses a nearly free-electron-like band structure, an isotropic s-wave energy gap, and a well-understood phonon-mediated pairing mechanism. The zero-temperature gap and critical temperature are to good approximation
        \begin{equation}
            \Delta_0 \approx 180\,\mu\mathrm{eV}\,,\qquad
            T_\mathrm{C} \approx 1.2\,\mathrm{K}\,.
            \label{eq:aluminum}
        \end{equation}
        Its long coherence length of order 1-2\,\textmu m, high electronic purity, and weak spin--orbit scattering make aluminum ideally suited for tunneling spectroscopy and mesoscopic superconducting transport. The comparatively small gap places typical microwave frequencies well below the pair-breaking threshold, enabling controlled photon-assisted processes without degrading superconductivity\footnote{The pair-breaking frequency of aluminium is given by $\nu\mathrm{pb}=2\Delta_0/h\approx 100\,\mathrm{GHz}$.}. Moreover, aluminum naturally forms reproducible aluminum-oxide tunnel barriers and reliably yields stable atomic contacts. It therefore provides a consistent and unified material platform for all transport phenomena discussed in this chapter.
        
    \subsubsection*{Microwave Drive Model}
    
        Many of the transport phenomena discussed in this chapter involve the presence of a time-dependent electromagnetic drive. To avoid repeated introductions of the same setup, we summarize here the general assumptions that apply to all subsequent descriptions. The drive is treated as a classical, externally imposed field. No cavity modes or backaction of the junction onto the field are considered. The entire voltage drop is assumed to occur across the junction, a convenient gauge choice. In consequence, the electromagnetic field enters only through the scalar potential in the tunneling Hamiltonian or via the Josephson phase evolution. The drive amplitude is taken to be small enough not to heat the electrodes, allowing both to remain in local thermal equilibrium with Fermi--Dirac distributions. Finally, the drive frequencies are chosen such that photon energy is way smaller than the pair-breaking energy, ensuring that Cooper pairs remain intact while the phase dynamics are driven coherently. In practice, frequencies in the microwave range up to about 20\,GHz are used.

        The spatially uniform microwave field is then given by 
        \begin{equation}
            V(t) = V_0 + A \cos (2\pi\nu t)\,,
            \label{eq:microwave}
        \end{equation}
        with a static component $V_0$, drive amplitude $A$, and frequency $\nu$. 
        
        The charge relevant for the electromagnetic phase is $q = m e$ with $m\in\{1,\,2,\,3,\,\dots\}$. For quasi-particles $m=1$, for Cooper-pair and single Andreev processes $m=2$, and for higher-order multiple Andreev reflections the effective transferred charge is $m>2$. However, the accumulated potential, determines the relevant electromagnetic phase factor
        \begin{align}
            \exp\!\left(-\ima\phi(t)\right) &= \exp\!\left( - \frac{\ima}{\hbar} \int_0^t q V(t')\, dt' \right) \\
            &= \!\exp\left(-\ima \phi_0(t)\right)\exp\!\left(\ima \alpha \sin(2\pi\nu t) \right)\,.
            \label{eq:microwave:phase-factor}
        \end{align}
        where $\alpha=qA/h\nu$ denotes the dimensionless modulation strength and $\phi_0(t) = q V_0 t / \hbar$ is the phase difference generated by the static drive.

        The phase factor is conveniently expanded using the Jacobi--Anger identity,
        \begin{equation}
            \exp\!\left(\ima\alpha \sin(2\pi\nu t)\right) = \sum_{n=-\infty}^{\infty} J_n(\alpha)\,
            \exp\!\left(\ima n\ 2\pi\nu t\right)\,
            \label{eq:microwave:jacobi-anger}
        \end{equation}
        where $J_n(\alpha)$ is the $n$-th Bessel function of the first kind. This harmonic decomposition will be used repeatedly in this chapter.


        
    \newpage

    \input{theory/micro.tex}
    \newpage

    \input{theory/macro.tex}
    \newpage

    \input{theory/meso.tex}
    \newpage

    \input{theory/stochastic.tex}
    \newpage

    \section{Experimental Realization}


    \section*{TODO}
    bin am 체berlegen die schemata maximal im Anhang zu zeigen (so poblig aus dem Poster screenshoten.) Ich finde man muss viel und lange erkl채ren was wann f체r vereinfachungen gelten und wie die Bilder gemeint sind. richtige physik l채sst sich damit nur schwer machen. Lieber mehr IV zeigen!
    \begin{itemize}
        \item do citations in theory introduction
        \item check consistency:
        \begin{itemize}
            \item quasi-particle
            \item Cooper-pair
            \item aluminum
            \item weak-coupling
            \item normal state
            \item - or --
            \item -- bei Modell namen (Tien--Gordon, Ginzburg--Landau)
        \end{itemize}
        \item check consistency seeblau100
    \end{itemize}

    \subsection*{theory}
    \begin{itemize}
        \item table with theories
    \end{itemize}

    \subsection*{macro}
    \begin{itemize}
        \item overlapping wave functions
        \item rscj shaltplan (mini)
        \item plots (a lot of them)
        \item do the citations
    \end{itemize}

    \subsection*{meso}
    \begin{itemize}
        \item check ABS section
        % \item AR-IV-tau
        % \item AR-IV-m
        % \item MAR-IV-tau
        % \item MAR-IV-m
        \item PAAR
        \item PAMAR
        \item do the citations
    \end{itemize}

    \subsection*{stochastic}
    \begin{itemize}
        \item alles
    \end{itemize}

    \subsection*{experiment and state of the art}
    \begin{itemize}
        \item alles
    \end{itemize}

    \newpage

