

    \section{Setup} \label{sec:stup}
        \subsection{cryostat and thermometer}
        \subsection{MCBJ} \label{subsec:mcbj}
            Danke Martin!

        \subsection{DC Cabling} \label{subsec:dc cabling}
        4point measurements
            \subsubsection*{copper powder filter}
            \subsubsection*{steel capillary cable}
            \subsubsection*{silver epoxy filter}

        \subsection{AC cabling}
            \subsubsection*{Attenuators}
            \subsubsection*{Antenna}
            \subsubsection*{stripline}

    \section{Data Acquisition}
        In this section i want to fucus on the used electronics. I scheme the measurement principle and the work on grounding. I'll also talk about the self-developed measurement program and go through the written drivers. A great deal of developing is done by Florian Kayatz, within his Hiwi. (cite: Flo) Finally I will also talk about the data treatment and processing.

        \subsection{DC Measurement Concept}
            As mentioned in Subsection \ref{subsec:dc cabling} a 4-point measurement principle is used. Given, by the former described setup, voltages down to roughly 1\,\textmu V should be measureable.
            - {layout}
            - {AD converter}
            - {Pre Amplifier}
        
        \subsection{Measurement Software}
            - P5 control
            - devices in appendix

        \subsection{Measurement Script}
            - explain iv\_script\_v2.py
            - test

        \subsection{Evaluation Script}
            - binning
            - data treatment

        \section{Drivers}
            into the appendix
            \subsection{p5 control}
            \subsection{GUI}
            \subsection{Femtos}
            \subsection{ADwin}
            \subsection{Bluefors Software}
            \subsection{Magnet}
            \subsection{Motor}
            \subsection{VNA}
            \subsection{Yoko}
            \subsection{Keysight}
        
        



